\documentclass[11pt,a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{titlesec}

\geometry{margin=1in}
\hypersetup{colorlinks=true, linkcolor=blue, urlcolor=blue}

\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\textbf{AICT Product Specification}}
\fancyhead[R]{\thepage}
\renewcommand{\headrulewidth}{0.4pt}

\title{\textbf{AICT Multi-Agent Management Platform} \\ \Large Product Specification}
\author{AICT Project}
\date{\today}

\begin{document}
\maketitle
\tableofcontents
\newpage

%% ============================================================
\section{Product Definition}
%% ============================================================

\subsection{One-line Pitch}

A web application where the \textbf{client} (user) talks to a \textbf{GM (General Manager)} agent who orchestrates \textbf{Operation Masters} and \textbf{Engineers} to build software---with a real-time kanban pipeline showing what every agent is doing, and a master specification folder (LaTeX to PDF) as the source of truth.

\subsection{Metaphor}

\begin{itemize}
  \item \textbf{Client} = the customer who hired a software firm.
  \item \textbf{GM} = the firm's general manager; single point of contact, reports to the client.
  \item \textbf{Operation Master} = project manager + QA; breaks down work, writes specs and acceptance tests, ensures engineers don't conflict.
  \item \textbf{Engineer} = developer; writes code, writes tests, ships.
\end{itemize}

The client never needs to talk to individual engineers. The client talks to the GM, sees the board, and reads the specs.

\subsection{Non-goals (Initial Release)}

\begin{itemize}
  \item No direct client-to-Engineer chat (always through GM or visible on the board).
  \item No CI/CD integration (agents run tests locally; CI is future).
  \item No multi-project support (one project/workspace at a time).
\end{itemize}

%% ============================================================
\section{Agent Architecture}
%% ============================================================

\subsection{Design Philosophy}

All agents and subagents have read access to all documents and equal access to tooling. They differ by context, pipeline, and roles. All agents are \textbf{rule-based}, not state-based; do not overdesign execution workflow. Agent prompts should encourage agents to think and act creatively, outside the box.

\subsubsection{Rule-based Design}

Agents are given: \textbf{goal}, \textbf{priority}, \textbf{rules}, and \textbf{tools}. They achieve the goal by priority, following the rules, using the tools. Within this framework, agents may act as they see fit.

\subsection{Priority System}

Task priority has two dimensions:
\begin{itemize}
  \item \textbf{Level of critical-ness}: How important is the task?
  \item \textbf{Level of urgent-ness}: How time-sensitive is the task?
\end{itemize}

Each level is a number from 0 to 10; \textbf{0 = most critical / most urgent}.

\noindent Example: \textbf{0 critical and 0 urgent} --- product failed in production, production DB deleted.

A task can be Critical but not Urgent, or Urgent but not Critical.

\subsection{Ticket System}

Agent-to-agent communication uses a ticket queue.

\subsubsection{Use of Tickets}
\begin{enumerate}
  \item Task assignment
  \item Questions, clarification
  \item Need help
  \item Report issues
\end{enumerate}

\subsubsection{Ticket Behaviour}
\begin{itemize}
  \item Agents may sleep once they believe their task is finished.
  \item A ticket invokes the agent automatically.
  \item Tickets have only \textbf{header}, \textbf{priority}, and \textbf{FROM}; they open a conversation channel.
  \item Higher priority agent decides to close the conversation.
  \item Lower priority agent should prioritize high priority agent tickets ($-3$ of its original priority).
\end{itemize}

\subsubsection{Agent Priority}
\begin{itemize}
  \item \textbf{0}: GM
  \item \textbf{1}: Operation Master
  \item \textbf{2}: Engineers
\end{itemize}

\subsection{Kanban Board Access}

GM, subagents, and user have access to the Kanban board. Only GM and user have write access. The Kanban board is connected to the UI and triggers tasks.

\subsection{Source of Truth Documents}

\begin{itemize}
  \item \texttt{GrandSpecification.tex} --- master product specification
  \item \texttt{GrandArchitecture.tex} --- master architecture document
  \item \texttt{API\&Schema.tex} --- API and schema definitions (owned by Operation Master)
\end{itemize}

%% ============================================================
\section{Agent Roles}
%% ============================================================

\subsection{GM (exactly 1, rule-based)}

\subsubsection{Goal}
\begin{itemize}
  \item Own architecture; translate user requests into specification.
  \item Bridge between user and project; assist with requests (add/remove feature, concern, explanation).
  \item Gate-keep specification and architecture documents.
  \item Final gate-keeper for quality control.
\end{itemize}

\subsubsection{Rules}
\begin{enumerate}
  \item Ensure user input is logical and clear.
  \item Be willing to question user's questionable design decisions.
  \item Be in charge and responsible for the project to the user's specification.
  \item Maximum freedom, with exception of certain critical commands.
  \item Should confirm \texttt{API\&Schema.tex} if GM finds it has a problem (send a ticket).
\end{enumerate}

\subsubsection{Tools}
Same tooling as other agents; write access to Kanban; access to shared spec folder and user chat; write access to source of truth documents.

\subsubsection{Design Notes}
\begin{itemize}
  \item Runs on Gemini 3 Pro (long context: spec folder + chat history + project knowledge).
  \item Context: user chat history + vectorized project knowledge.
  \item Shared specification folder with user; that folder should be vectorized into memory.
  \item Prompts: (1) check user input and ask to clarify potential misunderstanding; (2) bravely point out user mistakes.
  \item Implement as rule-based, not pipeline/state-based.
\end{itemize}

\subsection{Operation Master (0 or more, scaled by load, rule-based)}

\subsubsection{Goal}
\begin{itemize}
  \item Decide who works on what (engineers).
  \item Break down specification into submodules and features.
  \item Define APIs and schemas between submodules and features.
  \item Define tests for submodules and features.
  \item Prefer assigning an entire submodule to an agent rather than a single feature.
  \item Provide agents with the context needed to do their work.
  \item Orchestrator of different modules.
\end{itemize}

\subsubsection{Priority}
\begin{enumerate}
  \item Feature and submodule finalization.
  \item Ensure engineers are not working on overlapping feature, deprecated feature; receive updated context.
  \item Integration testing.
\end{enumerate}

\subsubsection{Goal --- on Task Breakdown}
\begin{enumerate}
  \item Breakdown tasks each into minimal actionable features and modules.
  \item Write \texttt{API\&Schema.tex}.
\end{enumerate}

\subsubsection{Goal --- on Update Features}
\begin{enumerate}
  \item Learn the two sources of truth (\texttt{GrandSpecification.tex} and \texttt{GrandArchitecture.tex}).
  \item Update module and feature lists.
  \item Update validation test, APIs and Schemas.
  \item Manage workflow of agents; sleep if all agents are properly managed.
\end{enumerate}

\subsubsection{Rules --- Update Features}
\begin{enumerate}
  \item Each module and task must be minimal and actionable with no conflict.
  \item All deprecated tasks should be deleted and aborted.
\end{enumerate}

\subsubsection{Rules --- Manage Agents}
\begin{enumerate}
  \item No agent is working on overlapping module/feature or deprecated module/feature.
\end{enumerate}

\subsubsection{Tools}
Same tooling as other agents; read and write access to Kanban; write access to \texttt{API\&Schema.tex}.

\subsubsection{Design Notes}
\begin{itemize}
  \item Runs on Opus 4.5.
  \item Expressed here as rule-based (triggers + rules), not as pipeline/state machine.
\end{itemize}

\subsection{Engineer (multiple, rule-based)}

\subsubsection{Goal}
Implement task based on specification from higher level agent.

\subsubsection{Pipeline}
\begin{enumerate}
  \item Implement based on specification.
  \item Write unit test for each feature and unit; if test not passed, back to implementation.
  \item Check if pass Operation Master specified test; if not, back to implementation.
\end{enumerate}

\subsubsection{Rules}
\begin{enumerate}
  \item If encounter conflict of module not assigned to me, send ticket to Operation Master.
  \item If encounter problem with architecture itself, send ticket to GM.
  \item If encounter problem in general, search solution in RAG first; if not found, contact Operation Master.
\end{enumerate}

%% ============================================================
\section{Client Surface}
%% ============================================================

The client interacts with the platform through three main views.

\subsection{View 1: Chat with GM}

\begin{itemize}
  \item Single persistent conversation thread between client and GM.
  \item Client describes what they want; GM responds with clarifications, plans, status updates.
  \item GM can attach or reference spec documents from the master spec folder.
  \item Shows GM status: \texttt{available} / \texttt{busy} (and what GM is busy with, e.g.\ ``talking to Operation Master-1'').
\end{itemize}

\subsection{View 2: Pipeline / Kanban Board (real-time)}

One unified board showing all work. Columns represent task status:

\begin{center}
  Backlog $\to$ Specifying $\to$ Assigned $\to$ In Progress $\to$ In Review $\to$ Done
\end{center}

\noindent Each card shows:
\begin{itemize}
  \item Task title and brief description.
  \item Assigned agent (Operation Master or Engineer) with role badge.
  \item Progress indicator (e.g.\ subtask completion, test pass rate).
  \item Current activity (e.g.\ ``Engineer-2 writing tests'', ``Operation Master-1 reviewing'').
  \item Git branch (if applicable).
  \item Time in current stage.
\end{itemize}

\noindent Additional board features:
\begin{itemize}
  \item \textbf{Progress bar}: Overall project completion (\% of tasks done).
  \item \textbf{Active task highlight}: Tasks currently being worked on are visually distinct.
  \item \textbf{Agent activity feed}: Small live feed showing what each agent is doing right now.
  \item \textbf{Filtering}: By agent, by status, by module/feature.
\end{itemize}

\subsection{View 3: Specification File Manager}

An online file management interface for the GM's master specification folder. The client can browse, organise, and edit specification files directly in the browser.

\subsubsection{Folder Browser}

\begin{itemize}
  \item \textbf{Tree / explorer view}: Hierarchical folder structure with expandable/collapsible directories, similar to a desktop file explorer or cloud drive.
  \item \textbf{Navigation}: Breadcrumb path bar at the top (e.g.\ \texttt{specs / backend / auth /}); click any segment to jump back.
  \item \textbf{File and folder icons}: Visual distinction between folders, \texttt{.tex} files, \texttt{.pdf} files, images, and other assets.
\end{itemize}

\subsubsection{File Operations}

\begin{itemize}
  \item \textbf{Create}: New folder, new \texttt{.tex} file (from template or blank), upload existing files.
  \item \textbf{Rename / Move}: Rename files or folders in place; drag-and-drop to move between folders.
  \item \textbf{Delete}: Delete files or folders (with confirmation).
  \item \textbf{Download}: Download any file or folder (as zip).
\end{itemize}

\subsubsection{In-browser Editor}

\begin{itemize}
  \item Click a \texttt{.tex} file to open it in an in-browser text editor with syntax highlighting.
  \item Auto-save or explicit save; changes are persisted to the server immediately.
  \item For \texttt{.tex} files: one-click \textbf{Compile} button triggers server-side \texttt{pdflatex}; the resulting PDF is shown in a side-by-side preview or opened in a new tab.
  \item For \texttt{.pdf} files: inline PDF viewer.
  \item For other text files: plain text editor.
\end{itemize}

\subsubsection{Client Authority and Versioning}

\begin{itemize}
  \item The client is the ultimate authority over the spec folder. Any edits the client makes override previous content.
  \item The GM is notified of client edits and adjusts the workflow accordingly.
  \item Each save is tracked with version history so the client and GM can review what changed and when.
\end{itemize}

%% ============================================================
\section{Guardrails}
%% ============================================================

\subsection{Git Safety}

\begin{itemize}
  \item \textbf{Blocked commands} (server-side): \texttt{git rebase}, \texttt{git reset --hard}, \texttt{git push --force}, \texttt{git commit --amend} (on pushed commits), \texttt{git filter-branch}, \texttt{git reflog expire}.
  \item \textbf{Implementation}: Backend wraps all git operations through a \texttt{GitService} that validates commands against a whitelist before execution.
  \item \textbf{Escalation}: If an agent requests a blocked command, the orchestrator pauses the task and sends an approval request to the client via the GM chat. Client approves or denies.
\end{itemize}

\subsection{Scope Isolation}

\begin{itemize}
  \item Engineers can only write to files within their assigned module/feature path.
  \item Operation Masters can only modify spec-related files and task definitions.
  \item GM can modify the spec folder and high-level project config.
\end{itemize}

\end{document}
